### 2022-05-11 supplement.Rmd
Move `print_` functions to separate script

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = format_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) -> tabs1

@@

\renewcommand{\arraystretch}{1.5}

@@

```{r, jackknife, include=TRUE}
# Helper functions for printing results from Bayesian model as a table
print_res_table <- function(res,
                            label_1 = NULL,
                            label_2 = NULL,
                            label_col_1 = "label_1",
                            label_col_2 = "label_2") {
  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Hedges' $g$` = b_Intercept,
      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
  if (!is.null(label_2)) {
    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_2 := tmp)
    tab <- cbind(label_2_tab, tab)
  }
  if (!is.null(label_1)) {
    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_1 := tmp)
    tab <- cbind(label_1_tab, tab)
  }
  return(tab)
}

# Re-run the jackknife analysis only if requested
if (run$jackknife_analysis) {

@@

# Display the table
apa_table(
  tab_jackknife,
  align = "llcccc",
  caption = "Jackknife (leave-one-out) analysis",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, sensitivity_analysis, include=TRUE}
# Helper functions for printing results as a table
print_res_reg_table <- function(res_reg,
                                label_1,
                                label_2,
                                label_col_1,
                                label_col_2) {
  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Intercept` = b_Intercept,
      `Female - mixed` = b_gender2M1,
      `Male - female` = b_gender3M2,
      `Age (per year)` = b_age_c,
      `Habituation - VoE` = b_task2M1,
      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
  if (!is.null(label_2)) {
    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_2 := tmp)
    tab <- cbind(label_2_tab, tab)
  }
  if (!is.null(label_1)) {
    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_1 := tmp)
    tab <- cbind(label_1_tab, tab)
  }
  return(tab)
}

# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

@@

# Create forest plot
dat_gender %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_brm_gender,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_brm_gender,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_brm_gender$intercept),
      print_num(summ_brm_gender$intercept.lower),
      print_num(summ_brm_gender$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate( # Just to make the grid lines disappear
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = nrow(dat_gender) + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = nrow(dat_gender) + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

>>>>

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) -> tabs1

@@

@@

```{r, jackknife, include=TRUE}
# Re-run the jackknife analysis only if requested
if (run$jackknife_analysis) {

@@

# Display the table
apa_table(
  tab_jackknife,
  align = "llcccc",
  caption = "Jackknife (leave-one-out) analysis",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE
)
```

```{r, sensitivity_analysis, include=TRUE}
# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

@@

# Create forest plot
dat_gender %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_brm_gender,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_brm_gender,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_brm_gender$intercept),
      print_num(summ_brm_gender$intercept.lower),
      print_num(summ_brm_gender$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate( # Just to make the grid lines disappear
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = nrow(dat_gender) + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = nrow(dat_gender) + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )
